Postural developments mediate children's visual access to social information

### 2018-01-29 writeup-cogsci/cogsci2018_faceOnly_alessandro.Rmd
redoing naming anlayses

aroundNamings_Posture_Wrists <- d %>%
  group_by(subid) %>%
  mutate(detections = wristOP) %>%
  do(summarize.naming(.)) %>%
  group_by(subid, posture) %>%
  summarize(propWristsDetected = mean(detections)) %>%
  filter(!is.na(propWristsDetected)) %>%
  filter(!is.na(posture)) %>%
  group_by(posture) %>%
  multi_boot_standard(col = "propWristsDetected")

@@

```{r echo=FALSE, include=FALSE}
## Break down by before/after naming
### First for wrists
beforeNamings_Wrists <- d %>%
  group_by(subid) %>%
  mutate(detections = wristOP) %>%
  do(summarize.naming(.,window = c(-2,0))) %>%
  group_by(subid, age.grp)  %>%
  summarise(avgDetections = mean(detections, na.rm=TRUE))  %>%
  mutate(namingTime = "beforeNaming")

namings_Wrists <- d %>%
  group_by(subid) %>%
  mutate(detections = wristOP) %>%
  do(summarize.naming(.,window = c(0,2))) %>%
  group_by(subid, age.grp)  %>%
  summarise(avgDetections = mean(detections, na.rm=TRUE)) %>%
  mutate(namingTime = "afterNaming") %>%
  bind_rows(beforeNamings_Wrists)

### Now for faces
beforeNamings_Faces <- d %>%
  group_by(subid) %>%
  mutate(detections = faceMT) %>%
  do(summarize.naming(.,window = c(-2,0))) %>%
  group_by(subid, age.grp)  %>%
  summarise(avgDetections = mean(detections, na.rm=TRUE))  %>%
  mutate(namingTime = "beforeNaming")

namings_Faces <- d %>%
  group_by(subid) %>%
  mutate(detections = faceMT) %>%
  do(summarize.naming(.,window = c(0,2))) %>%
  group_by(subid, age.grp)  %>%
  summarise(avgDetections = mean(detections, na.rm=TRUE)) %>%
  mutate(namingTime = "afterNaming") %>%
  bind_rows(beforeNamings_Faces)

# Plot if you want to look
# p1=ggplot(namings_Faces, aes(x = factor(age.grp), y = avgDetections, col = age.grp)) +
#   geom_boxplot() +
#   ylab("Prop. faces") +
#   xlab("") +
#   theme_few() +
#   theme(legend.position="none") +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
#   facet_grid(~namingTime)
# 
# p2=ggplot(namings_Wrists, aes(x = factor(age.grp), y = avgDetections, col = age.grp)) +
#   geom_boxplot() +
#   ylab("Prop. wrists") +
#   xlab("") +
#   theme_few() +
#   theme(legend.position="none") +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
#   facet_grid(~namingTime)

# ggarrange(p1,p2) # not shown in .rmd

## output for text below \
naming_Wrists_Summary <-  namings_Wrists %>%
  spread(namingTime, avgDetections) %>%
  mutate(diffWrists = afterNaming - beforeNaming) %>%
  group_by(age.grp) %>%
  summarize(mean = mean(diffWrists), sd=sd(diffWrists))

naming_Faces_Summary <-  namings_Faces %>%
  spread(namingTime, avgDetections) %>%
  mutate(diffFaces = afterNaming - beforeNaming) %>%
  group_by(age.grp) %>%
  summarize(mean = mean(diffFaces), sd=sd(diffFaces)) # no room for SD maybe but still informative

@@

## Access to Faces and Hands During Labeling Events
Finally, we analyzed how face and wrist/hand detections changed during object labeling events as a function of infant's posture and orientation. Specfically, we analyzed a four-second window around each labeling event (e.g., "Look at the [zem]!"); these labeling events were hand-annotated and automatically synchronized with the frame-by-frame face detections. We found that infants' posture and orientations impacted the degree to which they saw their caregiver's face and wrist during a labeling event; infants who were sitting or standing were more likely to have access to this social information. However, this did not manifest in a direct change the presence of wrists/hands before vs. after naming events (average difference in proportion of wrists detected, 8 m.o. = `r round(naming_Wrists_Summary$mean[1],3)`, 12 m.o. = `r round(naming_Wrists_Summary$mean[2],3)`, 16 m.o. = `r round(naming_Wrists_Summary$mean[3],3)`) or in proportion of faces detected  (average difference in proportion of faces detected, 8 m.o. = `r round(naming_Faces_Summary$mean[1],3)`, 12 m.o. = `r round(naming_Faces_Summary$mean[2],3)`, 16 m.o. = `r round(naming_Faces_Summary$mean[3],3)`).

>>>>

###
aroundNamings_Posture_Wrists <- d %>%
  group_by(subid) %>%
  mutate(detections = wristOP) %>%
  do(summarize.naming(.)) %>%
  group_by(subid, posture) %>%
  summarize(propWristsDetected = mean(detections)) %>%
  filter(!is.na(propWristsDetected)) %>%
  filter(!is.na(posture)) %>%
  group_by(posture) %>%
  multi_boot_standard(col = "propWristsDetected")

@@

```{r include=FALSE, echo=FALSE}
# Compute proportion of faces/hands during naming events relative to baseline
## Faces 
faces_baseline<- d %>%
  group_by(subid, age.grp) %>%
  summarize(baselineDetections = mean(faceMT))
#
faces_naming <- d %>%
  group_by(subid) %>%
  mutate(detections = faceMT) %>%
  do(summarize.naming(.)) %>%
  group_by(subid, age.grp)  %>%
  summarize(namingDetections = mean(detections,na.rm=TRUE)) %>% 
  left_join(faces_baseline) %>%
  mutate(baselineDiff = namingDetections - baselineDetections)  %>%
  group_by(age.grp) %>%
  summarize(avgBaselineDiff = mean(baselineDiff))
## Wrists
wrists_baseline<- d %>%
  group_by(subid, age.grp) %>%
  summarize(baselineDetections = mean(faceMT))
#
wrists_naming <- d %>%
  group_by(subid) %>%
  mutate(detections = wristOP) %>%
  do(summarize.naming(.)) %>%
  group_by(subid, age.grp)  %>%
  summarize(namingDetections = mean(detections, na.rm=TRUE)) %>%
  left_join(wrists_baseline) %>%
  mutate(baselineDiff = namingDetections - baselineDetections)  %>%
  group_by(age.grp) %>%
  summarize(avgBaselineDiff = mean(baselineDiff))

@@

## Access to Faces and Hands During Labeling Events
Finally, we explored how face and wrist/hand detections changed during object labeling events as a function of infant's posture and orientation. Specfically, we analyzed a four-second window around each labeling event (e.g., "Look at the [zem]!"); these labeling events were hand-annotated and automatically synchronized with the frame-by-frame face detections. As before, we found that infants' posture and orientations impacted the degree to which they saw their caregiver's face and wrist during a labeling event; infants who were sitting or standing were more likely to have access to this social information. A full summary of the results can be seen in Figure \ref{fig:detByNaming}. However, we did not find that infants saw more faces or more wrists/hands during naming events relative to baseline (average difference in proportion of wrists detected, 8 m.o. = `r round(wrists_naming$avgBaselineDiff[1],3)`, 12 m.o. = `r round(wrists_naming$avgBaselineDiff[2],3)`, 16 m.o. = `r round(wrists_naming$avgBaselineDiff[3],3)`;  average difference in proportion of faces detected, 8 m.o. = `r round(faces_naming$avgBaselineDiff[1],3)`, 12 m.o. = `r round(faces_naming$avgBaselineDiff[2],3)`, 16 m.o. = `r round(faces_naming$avgBaselineDiff[3],3)`).
